intro

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added setup

>>>>

```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
# set knitr options
knitr::opts_chunk$set(out.width = "\\textwidth")

# load libraries
library(here) # for path independent file referencing
  # set top level directory to source file

  here::i_am("flag_project_root_CERED.txt")
library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown

```
